---
title: "Assignment 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, warning=FALSE}
options (scipen = 999)
library(tidyverse)
library(tidymodels)
library(tidytext)
library(janitor)
library(skimr)
library(vip)
library(parallel)  # - new 
library(doParallel) # - new 
library(rpart.plot)
library(textrecipes)
library(stringi)
library(xgboost)
```

```{r, message=FALSE, error=FALSE}
job_holdout <- read.csv("job_holdout.csv")
job_training <- read.csv("job_training.csv")

job_training <- job_training %>% janitor::clean_names()
```

```{r}
job_training %>% skimr::skim_without_charts()
```


## Clean data

### Remove unimportant data
```{r, message=FALSE, warning=FALSE}
job_training <- job_training %>% select(-location)
job_holdout <- job_holdout %>% select(-location)
```



### Replace variables with their binary variables
```{r, message=FALSE, warning=FALSE}
job_training <- job_training %>%
  mutate(has_salary_range = ifelse(is.na(salary_range), 0, 1))%>%
  select(-salary_range)

job_holdout <- job_holdout %>%
  mutate(has_salary_range = ifelse(is.na(salary_range), 0, 1))%>%
  select(-salary_range)


job_training <- job_training %>%
  mutate(has_department = ifelse(is.na(department), 0, 1)) %>%
  select(-department)

job_holdout <- job_holdout %>%
  mutate(has_department = ifelse(is.na(department), 0, 1)) %>%
  select(-department)

```


### Work on the "Not applicables'
```{r, message=FALSE, warning=FALSE}
#---
job_training$employment_type[is.na(job_training$employment_type)] <- "Other"
job_holdout$employment_type[is.na(job_holdout$employment_type)] <- "Other"

#---
job_training$required_experience[is.na(job_training$required_experience)] <- "Not Applicable"
job_holdout$required_experience[is.na(job_holdout$required_experience)] <- "Not Applicable"

#---
job_training$required_education[is.na(job_training$required_education)] <- "Unspecified"
job_holdout$required_education[is.na(job_holdout$required_education)] <- "Unspecified"

```


### Target encoding
```{r, message=FALSE, warning=FALSE}
####---
industry_fraud <- job_training %>%
  group_by(fraudulent, industry) %>%
  select(industry) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from= n, values_fill = 0.0) %>%
  mutate(industry_pct_fraud = `1`/(`1`+`0`)) %>%
  select(industry, industry_pct_fraud)

job_training <- job_training %>%
  left_join(industry_fraud) %>%
  select(-industry)

job_holdout <- job_holdout %>%
  left_join(industry_fraud) %>%
  select(-industry)

remove(industry_fraud)


###---
job_function_fraud <- job_training %>%
  group_by(fraudulent, job_function) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n, values_fill = 0.0) %>%
  mutate(jfunction_pct_fraud = `1`/(`0`+`1`)) %>%
  select(job_function, jfunction_pct_fraud)

job_training <- job_training %>%
  left_join(job_function_fraud) %>%
  select(-job_function)

job_holdout <- job_holdout %>%
  left_join(job_function_fraud) %>%
  select(-job_function)

remove(job_function_fraud)

```


### Add number of words used to describe the company and the job position
```{r, message=FALSE, warning=FALSE}
job_training <- job_training %>%
  mutate(company_profile_words = ifelse(is.na(company_profile), 0, str_count(company_profile, boundary("word"))),description_words = 
      ifelse(is.na(description), 0, str_count(description, boundary("word"))),
    requirement_words =
      ifelse(is.na(requirements), 0, str_count(requirements, boundary("word"))),
    benefit_words = ifelse(is.na(benefits), 0, str_count(benefits, boundary("word"))))

  
job_holdout <- job_holdout %>%
  mutate(company_profile_words = ifelse(is.na(company_profile), 0, str_count(company_profile, boundary("word"))),description_words = 
      ifelse(is.na(description), 0, str_count(description, boundary("word"))),
    requirement_words =
      ifelse(is.na(requirements), 0, str_count(requirements, boundary("word"))),
    benefit_words = ifelse(is.na(benefits), 0, str_count(benefits, boundary("word"))))
```


### Clean text data
```{r, message=FALSE, warning=FALSE}
job_training <- job_training %>%
  mutate(title = stri_replace_all_regex(title, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(company_profile = stri_replace_all_regex(company_profile, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(description = stri_replace_all_regex(description, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(requirements = stri_replace_all_regex(requirements, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(benefits = stri_replace_all_regex(benefits, '[^a-zA-Z0-9*$]', " "))

job_holdout <- job_holdout %>%
  mutate(title = stri_replace_all_regex(title, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(company_profile = stri_replace_all_regex(company_profile, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(description = stri_replace_all_regex(description, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(requirements = stri_replace_all_regex(requirements, '[^a-zA-Z0-9*$]', " ")) %>%
  mutate(benefits = stri_replace_all_regex(benefits, '[^a-zA-Z0-9*$]', " "))
```


### to factor
```{r, message=FALSE, warning=FALSE}
training_df <- job_training %>%
  mutate_if(is.character, as_factor) %>%
  mutate(fraudulent = as.factor(fraudulent)) %>%
  mutate(telecommuting = as.factor(telecommuting)) %>%
  mutate(has_company_logo = as.factor(has_company_logo)) %>%
  mutate(has_questions = as.factor(has_questions)) %>%
  mutate(has_salary_range = as.factor(has_salary_range)) %>%
  mutate(has_department = as.factor(has_department))

holdout_df <- job_holdout %>%
  mutate_if(is.character, as_factor) %>%
  mutate(telecommuting = as.factor(telecommuting)) %>%
  mutate(has_company_logo = as.factor(has_company_logo)) %>%
  mutate(has_questions = as.factor(has_questions)) %>%
  mutate(has_salary_range = as.factor(has_salary_range)) %>%
  mutate(has_department = as.factor(has_department))

```

```{r}
skimr::skim_without_charts(data=training_df)
```

## Split Data
```{r}
set.seed(42)
df_split <- initial_split(data = training_df, prop = 0.7, strata = fraudulent)

train <- training(df_split)
test <- testing(df_split)

set.seed(42)
train_fold <- vfold_cv(data = train, v = 5)
```


## Data Exploration

### Target Variable - bar graph
```{r, message=FALSE, warning=FALSE}
job_training %>%
  ggplot(aes(fraudulent)) +
  geom_bar(stat = "count") +
  labs(title = "Distribution of Fraudulent Jobs")
```

### Target variable - table
```{r, message=FALSE, warning=FALSE}
job_training %>%
  group_by(fraudulent) %>%
  summarize(n=n()) %>%
  mutate(pct = round(n/sum(n), 2))
```


### Correlation
```{r, message=FALSE, warning=FALSE}
job_training %>%
  select(where(is.numeric), -job_id) %>%
  lares::corr_var(fraudulent)
```


### Numeric Data
```{r, message=FALSE, warning=FALSE}

plot_numeric <- function(col){
  training_df %>%
    ggplot(aes(x=fraudulent, y=!!as.name(col))) +
    geom_boxplot()
}

for (column in names(training_df %>% select(where(is.numeric), -job_id))){
  print(plot_numeric(column))
}
  


```

#### Numeric Data - Percentage fraud by category

**Industry percentage fraud and job function percentage fraud**
```{r, message=FALSE, warning=FALSE}

training_df %>%
  select(fraudulent, where(is.numeric), -job_id) %>%
  group_by(fraudulent) %>%
  summarize(industry_pct = round(mean(industry_pct_fraud), 2),
            job_function_pct = round(mean(jfunction_pct_fraud), 2)) %>%
  ungroup() %>%
  mutate_if(is.numeric, round, 2)
```

**Number of words used to describe company profile, job description**
**job requirements, and benefits**
```{r, message=FALSE, warning=FALSE}

training_df %>%
  select(fraudulent, where(is.numeric), -job_id) %>%
  group_by(fraudulent) %>%
  summarize(company_profile = round(mean(company_profile_words), 0),
            description = round(mean(description_words), 0),
            requirement = round(mean(requirement_words), 0),
            benefit = round(mean(benefit_words), 0)) %>%
  ungroup() %>%
  mutate_if(is.numeric, round, 2)
```

### factor Data
```{r, message=FALSE, warning=FALSE}
plot_factor <- function(col){
  training_df %>%
    ggplot(., aes(!!as.name(col))) +
    geom_bar(aes(fill = fraudulent), position = "fill") +
    coord_flip()
}

for(column in names(training_df %>%
                    select(telecommuting, has_company_logo, has_questions,
                           employment_type, required_experience, required_education,
                           has_salary_range,has_department)))
{
  print(plot_factor(column))
}
```

#### Factor data - percentage fraud by category

**Telecommuting**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, telecommuting) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(telecommuting, legit, fraud, pct) %>%
  arrange(desc(pct))

```

**has_company_logo**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, has_company_logo) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(has_company_logo, legit, fraud, pct)%>%
  arrange(desc(pct))

```

**has_questions**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, has_questions) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(has_questions, legit, fraud, pct)%>%
  arrange(desc(pct))

```

**employment_type**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, employment_type) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(employment_type, legit, fraud, pct)%>%
  arrange(desc(pct))

```

**required_experience**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, required_experience) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(required_experience, legit, fraud, pct)%>%
  arrange(desc(pct))

```

**required_education**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, required_education) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(required_education, legit, fraud, pct)%>%
  arrange(desc(pct))

```


**has_salary_range**
```{r, message=FALSE, warning=FALSE}
training_df %>%
  select(where(is.factor)) %>%
  group_by(fraudulent, has_salary_range) %>%
  summarize(n=n()) %>%
  pivot_wider(names_from = fraudulent, values_from = n) %>%
  mutate(pct = round(`1`/(`0`+`1`), 2), legit = `0`, fraud = `1`) %>%
  select(has_salary_range, legit, fraud, pct)%>%
  arrange(desc(pct))

```

## Model Creation

### Random Forest
```{r, message=FALSE, warning=FALSE}

training_recipe <- training_df %>%
  recipe(fraudulent ~.) %>%
  update_role(job_id, new_role = "IGNORE") %>%
  step_unknown(all_nominal_predictors()) %>%
  step_impute_mean(all_numeric_predictors()) %>%
  step_tokenize(title, company_profile, description, requirements, benefits) %>%
  step_stopwords(title, company_profile, description, requirements, benefits) %>%
  step_tokenfilter(title, company_profile, description, requirements, benefits, max_tokens = 5) %>%
  step_tf(title, company_profile, description, requirements, benefits) %>%
  step_other(all_nominal_predictors(), threshold = 0.01)


rf_model <- rand_forest(min_n = tune(), trees = tune()) %>%
  set_mode("classification") %>%
  set_engine("ranger", importance = "permutation")

rf_workflow <- workflow() %>%
  add_recipe(training_recipe) %>%
  add_model(rf_model)

all_cores <- detectCores(logical = FALSE)
cl <- makeCluster(all_cores)
doParallel::registerDoParallel(cl)
rf_grid <- grid_regular(
  min_n(),
  trees(c(5,20)),
  levels = 5
)

rf_tuning_results <- rf_workflow %>%
  tune_grid(
    resamples = train_fold,
    grid = rf_grid
    )

rf_model <- rf_workflow %>%
  finalize_workflow(select_best(rf_tuning_results))

rf_fit <- fit(rf_model, train)
```


### Tuning Metrics

**Tuning metrics - Table**
```{r, message=FALSE, warning=FALSE}
rf_tuning_results_table <- rf_tuning_results %>%
  collect_metrics()%>%
  mutate_if(is.numeric, round, 3)%>%
  select(.metric, trees, min_n, mean, std_err) %>%
  arrange(desc(mean))

rf_tuning_results_table %>%
  filter(.metric == "roc_auc")
```


**Tuning metrics - Effect of "trees"**
```{r, message=FALSE, warning=FALSE}
rf_tuning_results_table %>%
  ggplot(aes(trees, mean)) +
  geom_line() +
  facet_wrap(~.metric, scales="free", nrow = 2)
```

**Tuning metrics - Effect of "min_n"**
```{r, message=FALSE, warning=FALSE}
rf_tuning_results_table %>%
  ggplot(aes(min_n, mean)) +
  geom_line() +
  facet_wrap(~.metric, scales="free", nrow = 2)
```

### Fit model metrics

**Fit model metrics - Scores**
```{r, message=FALSE, warning=FALSE}
options(yardstick.event_first = FALSE)
rf_train_scored <- predict(rf_fit, train, type = "prob") %>%
  bind_cols(predict(rf_fit, train)) %>%
  bind_cols(train) %>%
  mutate(model = "random forest", scored_on = "train data") %>%
  select(job_id, model, scored_on, fraudulent, .pred_class, .pred_1)

rf_test_scored <- predict(rf_fit, test, type = "prob") %>%
  bind_cols(predict(rf_fit, test)) %>%
  bind_cols(test) %>%
  mutate(model = "random forest", scored_on = "test data") %>%
  select(job_id, model, scored_on, fraudulent, .pred_class, .pred_1)

rf_scored <- rf_train_scored %>%
  bind_rows(rf_test_scored)

```


**Fit model metrics - important variables**
```{r, message=FALSE, warning=FALSE}
rf_fit %>%
  pull_workflow_fit() %>%
  vip(10)
```



**Fit model metrics - Classification Matrix**
```{r, message=FALSE, warning=FALSE}
rf_train_scored %>%
  conf_mat(fraudulent, .pred_class) %>%
  autoplot(type="heatmap") +
  labs(title = "Classification Matrix - Train Data")
```
```{r, message=FALSE, warning=FALSE}
rf_test_scored %>%
  conf_mat(fraudulent, .pred_class) %>%
  autoplot(type="heatmap") +
  labs(title = "Classification Matrix - Test Data")
```

**Fit model metrics - ROC_AUC Curve**
```{r, message=FALSE, warning=FALSE}
rf_scored %>%
  group_by(scored_on) %>%
  roc_curve(fraudulent, .pred_1) %>%
  autoplot() +
  geom_vline(xintercept = 0.1, color="blue", size=0.5)
```

**Metrics - accuracy, kap, mn_log_loss and roc_auc**
```{r, message=FALSE, warning=FALSE}
rf_metrics_roc_logloss_etc <- rf_test_scored %>%
  metrics(fraudulent, .pred_1, estimate =.pred_class) %>%
  mutate(model = "random forest", scored_on = "test data") %>%
  bind_rows(
    rf_train_scored %>%
      metrics(fraudulent, .pred_1, estimate =.pred_class) %>%
      mutate(model = "random forest", scored_on = "train data")
  ) %>%
  group_by(model, scored_on) %>%
  pivot_wider(names_from = .metric, values_from =  .estimate) %>%
  select(model, .estimator, scored_on, accuracy, kap, mn_log_loss, roc_auc) %>%
  mutate_if(is.numeric, round, 2)

rf_metrics_roc_logloss_etc

```


**Metrics - precision and recall**
```{r, message=FALSE, warning=FALSE}
rf_metrics_precision_and_recall <- rf_train_scored %>%
  precision(truth = fraudulent, estimate = .pred_class) %>%
  bind_rows(rf_train_scored %>%
              recall(truth = fraudulent, estimate = .pred_class)) %>%
  mutate(model = "random forest", scored_on = "train data") %>%
  bind_rows(
    rf_test_scored %>%
      precision(truth = fraudulent, estimate = .pred_class) %>%
      bind_rows(rf_test_scored %>%
                  recall(truth = fraudulent, estimate = .pred_class)) %>%
      mutate(model = "random forest", scored_on = "test data")  
  ) %>%
  group_by(model, scored_on) %>%
  pivot_wider(names_from = .metric, values_from = .estimate) %>%
  select(model, .estimator, scored_on, precision, recall) %>%
  mutate_if(is.numeric, round, 2)

rf_metrics_precision_and_recall

```


**Fit model metrics - Threshold**
```{r, message=FALSE, warning=FALSE}
rf_test_scored %>%
  roc_curve(fraudulent, .pred_1) %>%
  mutate(fpr = 1-round(specificity, 2),
         tpr = round(sensitivity, 3),
         threshold = 1 - round(.threshold, 3)) %>%
  select(fpr, tpr, threshold) %>%
  group_by(fpr) %>%
  summarize(tpr = max(tpr),
          threshold = max(threshold)) %>%
  ungroup() %>%
  mutate(precision = tpr/(fpr + tpr)) %>%
  mutate_if(is.numeric, round, 2) %>%
  arrange(fpr) %>%
  filter(fpr <= 0.1)

```




### XGBoost
```{r, message=FALSE, warning=FALSE}
xgboost_recipe <- training_df %>%
  recipe(fraudulent ~.) %>%
  update_role(job_id, new_role = "IGNORE") %>%
  step_nzv(all_predictors()) %>%
  step_unknown(all_nominal_predictors()) %>%
  step_impute_mean(all_numeric_predictors()) %>%
  step_tokenize(title, company_profile, description, requirements, benefits) %>%
  step_stopwords(title, company_profile, description, requirements, benefits) %>%
  step_tokenfilter(title, company_profile, description, requirements, benefits, max_tokens = 5) %>%
  step_tf(title, company_profile, description, requirements, benefits) %>%
  step_other(all_nominal_predictors(), threshold = 0.05) %>%
  step_string2factor(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors())


xgboost_model <- boost_tree(trees = 5,
                            tree_depth = tune(),
                            learn_rate = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("classification")

xgboost_wf <- workflow() %>%
  add_recipe(xgboost_recipe) %>%
  add_model(xgboost_model)

xgboost_grid <- grid_regular(
  tree_depth(),
  learn_rate(),
  levels=5)

all_cores <- detectCores(logical = FALSE)
cl <- makeCluster(all_cores)
doParallel::registerDoParallel(cl)

xgboost_tuning_results <- xgboost_wf %>%
  tune_grid(
    resamples = train_fold,
    grid = xgboost_grid
  )

xgboost_model <- xgboost_wf %>%
  finalize_workflow(select_best(xgboost_tuning_results))

xgboost_fit <- fit(xgboost_model, train)
```

**Tuning metrics Scores - Table**
```{r, message=FALSE, warning=FALSE}
xgboost_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round, 3) %>%
  select(.metric, tree_depth, learn_rate, mean, std_err) %>%
  filter(.metric == "roc_auc") %>%
  arrange(desc(mean))
```


**Tuning metrics Scores - Effects of "tree_depth"**
```{r, message=FALSE, warning=FALSE}
xgboost_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round, 3) %>%
  select(.metric, tree_depth, learn_rate, mean, std_err) %>%
  ggplot(aes(tree_depth, mean)) +
  geom_line() +
  facet_wrap(~.metric, scales = "free", nrow = 2)
```

**Tuning metrics Scores - Effect of "learn_rate"**
```{r, message=FALSE, warning=FALSE}
xgboost_tuning_results %>%
  collect_metrics() %>%
  mutate_if(is.numeric, round, 3) %>%
  select(.metric, tree_depth, learn_rate, mean, std_err) %>%
  ggplot(aes(learn_rate, mean)) +
  geom_line() +
  facet_wrap(~.metric, scales = "free", nrow = 2)
```

### Fit model metrics
```{r, message=FALSE, warning=FALSE}
options(yardstick.event_first = FALSE)
xgboost_train_scored <- predict(xgboost_fit, train, type = "prob") %>%
  bind_cols(predict(xgboost_fit, train)) %>%
  bind_cols(train) %>%
  mutate(model = "xgboost", scored_on = "train data") %>%
  select(job_id, model, scored_on, fraudulent, .pred_class, .pred_1)

xgboost_test_scored <- predict(xgboost_fit, test, type = "prob") %>%
  bind_cols(predict(xgboost_fit, test)) %>%
  bind_cols(test) %>%
  mutate(model = "xgboost", scored_on = "test data") %>%
  select(job_id, model, scored_on, fraudulent, .pred_class, .pred_1)

xgboost_scored <- xgboost_train_scored %>%
  bind_rows(xgboost_test_scored)

```


**Important variables**
```{r, message=FALSE, warning=FALSE}
xgboost_fit %>%
  pull_workflow_fit() %>%
  vip(10)
```


**Fit model metrics - ROC_AUC Curve**
```{r, message=FALSE, warning=FALSE}
xgboost_scored %>%
  group_by(scored_on) %>%
  roc_curve(fraudulent, .pred_1) %>%
  autoplot() +
  geom_vline(xintercept = 0.1, color="blue", size=0.5)
```

**Metrics - accuracy, kap, mn_log_loss and roc_auc**
```{r, message=FALSE, warning=FALSE}
xgboost_metrics_roc_logloss_etc <- xgboost_test_scored %>%
  metrics(fraudulent, .pred_1, estimate =.pred_class) %>%
  mutate(model = "xgboost", scored_on = "test data") %>%
  bind_rows(
    xgboost_train_scored %>%
      metrics(fraudulent, .pred_1, estimate =.pred_class) %>%
      mutate(model = "xgboost", scored_on = "train data")
  ) %>%
  group_by(model, scored_on) %>%
  pivot_wider(names_from = .metric, values_from =  .estimate) %>%
  select(model, .estimator, scored_on, accuracy, kap, mn_log_loss, roc_auc) %>%
  mutate_if(is.numeric, round, 2)

xgboost_metrics_roc_logloss_etc
```


**Metrics - precision and recall**
```{r, message=FALSE, warning=FALSE}
xgboost_metrics_precision_and_recall <- xgboost_train_scored %>%
  precision(truth = fraudulent, estimate = .pred_class) %>%
  bind_rows(rf_train_scored %>%
              recall(truth = fraudulent, estimate = .pred_class)) %>%
  mutate(model = "xgboost", scored_on = "train data") %>%
  bind_rows(
    xgboost_test_scored %>%
      precision(truth = fraudulent, estimate = .pred_class) %>%
      bind_rows(rf_test_scored %>%
                  recall(truth = fraudulent, estimate = .pred_class)) %>%
      mutate(model = "xgboost", scored_on = "test data")  
  ) %>%
  group_by(model, scored_on) %>%
  pivot_wider(names_from = .metric, values_from = .estimate) %>%
  select(model, .estimator, scored_on, precision, recall) %>%
  mutate_if(is.numeric, round, 2)

xgboost_metrics_precision_and_recall
```


**Fit model metrics - threshold**
```{r, message=FALSE, warning=FALSE}
rf_test_scored %>%
  roc_curve(fraudulent, .pred_1) %>%
  mutate(fpr = 1-round(specificity, 2),
         tpr = round(sensitivity, 3),
         threshold = 1 - round(.threshold, 3)) %>%
  select(fpr, tpr, threshold) %>%
  group_by(fpr) %>%
  summarize(tpr = max(tpr),
          threshold = max(threshold)) %>%
  ungroup() %>%
  mutate(precision = round(tpr/(fpr + tpr), 2)) %>%
  select(fpr, tpr, precision, threshold) %>%
  arrange(fpr) %>%
  filter(fpr <= 0.1)

```


## Model Comparison

### ROC_AUC curve
```{r, message=FALSE,warning=FALSE}
rf_scored %>%
  bind_rows(xgboost_scored) %>%
  filter(scored_on == "test data") %>%
  group_by(model)%>%
  roc_curve(fraudulent, .pred_1) %>%
  autoplot() +
  geom_vline(xintercept = 0.1, color = "blue", size = 0.5)

```

### Metrics
```{r, message=FALSE, warning=FALSE}
precision_and_recall <- rf_metrics_precision_and_recall %>%
  bind_rows(xgboost_metrics_precision_and_recall)

rf_scored %>%
  bind_rows(xgboost_scored) %>%
  group_by(model, scored_on) %>%
  metrics(fraudulent, .pred_1, estimate = .pred_class ) %>%
  pivot_wider(names_from = .metric, values_from = .estimate) %>%
  select(model, .estimator, scored_on, accuracy, kap, mn_log_loss, roc_auc) %>%
  mutate_if(is.numeric, round, 3) %>%
  left_join(precision_and_recall) %>%
  select(model, scored_on, accuracy, kap, mn_log_loss, roc_auc, precision, recall)

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results=FALSE}
rf_predictions <- predict(rf_fit, holdout_df, type = "prob") %>%
  bind_cols(holdout_df) %>%
  select(job_id, fraudulent = .pred_1)

write_csv(rf_predictions, "rf.csv")


xgboost_predictions <- predict(xgboost_fit, holdout_df, type = "prob") %>%
  bind_cols(holdout_df) %>%
  select(job_id, fraudulent = .pred_1)

write_csv(xgboost_predictions, "xgboost.csv")
```



